Tesseroids: forward modeling gravitational fields in spherical coordinates

### 2015-02-28 manuscript.tex
Typo fix

The biggest bottlenecks for the numerical integration are
the number of point masses used
and he evaluation of the trigonometric functions in
equations~\ref{eq:tesspot}-\ref{eq:tesstensor} inside the inner loops.
Better performance is achieved
by pre-computing the sine and cosine of latitudes
and moving some trigonometric function evaluations
to the outer loops.

>>>>

The biggest bottlenecks for the numerical integration are
the number of point masses used
and the evaluation of the trigonometric functions in
equations~\ref{eq:tesspot}-\ref{eq:tesstensor} inside the inner loops.
Better performance is achieved
by pre-computing the sine and cosine of latitudes
and moving some trigonometric function evaluations
to the outer loops.
